---
title: "Checking checking"
output: html_document
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(checkr)
library(magrittr)

# A simple checker function

# to put the info in a file
# knitr::opts_chunk$set(exercise.checker = checkr::check_info_to_file)

# to process it in the Rmd document
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

## Example 1

Modify the code to add two and two:

```{r, example_0, exercise = TRUE}
1 + 3
```

```{r example_0-solution}
2 + 2
```

```{r example_0-check}
test_0 <- find_call("whatever + whatever", "use addition (+)")
test_1 <- find_call("2 + whatever", "first argument should be two ")
test_2 <- find_call("whatever + 2", "second argument should also be two")
test_3 <- find_call("2 + 2", "remember to add two plus two")
USER_CODE %>% test_0 %>% test_1 %>% test_2 %>% test_3
soln_test(USER_CODE, SOLN_CODE,
             res = final_,
             same_num(res))
```

## Example 2

Use R to compute the length of the hypotenuse of a right triangle with edges of length 3 and 4.

```{r example-triangle, exercise = TRUE}
# your code goes here
```

```{r example-triangle-solution}
sqrt(3^2 + 4^2)
```

```{r example-triangle-check}
test_1 <- find_call("whatever ^ 2", "need to square the lengths")
test_A <- find_call("2 ^ whatever")
test_2 <- find_call("3 ^ 2", "one of the lengths is 3")
test_3 <- find_call("4 ^ 2", "one of the lengths is 4")
test_4 <- find_call("sqrt()", "you'll have to use the square-root function to get the length.")
test_5 <- find_call("whatever + whatever", "remember to add the squares")
test_6 <- find_value(match_number(5, range = c(4.99, 5.01)), "the overall result should be 5.")
USER_CODE %>% test_A %>% was_mistake("you've reversed the arguments to '^'") %>%
  test_1 %>% test_2 %>% test_3 %>% test_4 %>% test_5 %>% test_6

```

## Example 3

Fill in the code to create this plot:

```{r, echo = FALSE, out.width = "30%"}
ggplot(mtcars, aes(x = hp, y = mpg)) + 
  geom_point(aes(color = carb))
```

```{r, mtcarplot, exercise=TRUE}
ggplot(mtcars, aes( x = ___ , y = ___ )) + geom_point()
```

```{r mtcarplot-solution}
ggplot(mtcars, aes(x=hp, y = mpg)) + geom_point(aes(color = carb))
```

```{r mtcarplot-check}
test_1 <- find_call("aes(y = mpg)", message = "mpg should be the y aesthetic")
test_2 <- find_call("aes(x = hp, y = mpg)", message = "set the aesthetics via aes() to put the right variable on each axis.")
test_3 <- find_call("aes(color = carb)", "map carb to the color aethetic")
USER_CODE %>% test_1
USER_CODE %>% test_1 %>% test_2
USER_CODE %>% test_3
```

## Example 4

Use `dplyr` statements to find the mean hp of 4 cyl cars.

```{r mtcardplyr, exercise = TRUE}
require(dplyr)
mtcars %>%
  filter(cyl == 4) %>%
  summarise(mn = mean(hp))
```

```{r mtcardplyr-solution}
require(dplyr)
mtcars %>%
  filter(cyl == 4) %>%
  summarise(mn = mean(hp))
```

```{r mtcardplyr-check}
# Note that even though summarise() is used with a named argument
# we can disregard the name
test_1 <- find_statement("mtcars", "use the <mtcars> data frame")
test_2 <- find_call("filter()")
test_3 <- check_argument("cyl == grab_this", match_number(4, hint = TRUE))
test_4 <- find_statement("cyl == 4", "it's the cylinders we want to restrict to 4")
test_5 <- find_call("summarise(whatever)", "use summarise to compute the mean")
test_6 <- find_call("mean(hp)", "calculate the mean horsepower")

USER_CODE %>% test_1 %>% test_2 %>% test_3 %>% test_4 %>% test_5 %>% test_6

soln_test(USER_CODE, SOLN_CODE,
          a = final_,
          same_num(nrow(a)),
          same_num(length(a)))


```

## Example 4: 

> NOTE in DRAFT. I commented out the `soln_test()` line since it produces an error, "test_1 not found." But clearly `test_1` is there.  

Get the `CPS85` data from the `mosaicData` package using 
```r
data("CPS85", package = "mosaicData")
```

Then build a model of wage as a response, using enough explanatory variables to get $R^2 > 0.25$.
Give your model the name `my_mod`.

Note, this has already been filled in so that I can get the user code without any work.
```{r cps85r, exercise = TRUE}
data("CPS85", package = "mosaicData")
my_mod <- lm(wage ~ sector *educ + sex + married + union, data = CPS85)
```

```{r cps85r-solution}
data("CPS85", package = "mosaicData")
my_mod <- lm(wage ~ sector *educ + sex + married + union, data = CPS85)
```

```{r cps85r-check}
test_1 <- find_call("data('CPS85')", "remember to use data() to bring in the data." )
test_2 <- find_call("wage ~ whatever", "wage should be the response variable")
final_val <- check_value(test = function(mod) ifelse(mosaic::rsquared(mod) > .25, "", "not good enough"), message = "your R^2 is not good enough. Try some new explanatory terms.")
USER_CODE %>% test_1 %>% test_2 %>% final_val
#soln_test(USER_CODE, SOLN_CODE,
#          a = test_1,
#          same_num(mosaic::rsquared(a) > .25))
```

## Example 7

This is miscellaneous stuff just to illustrate code checking.  The tests will pass, as is. Modify the code to trigger fail messages.

> Assign the name `x` to 7. Then compute $x^2 + 1$ and assign the name `y` to $\cos x$.

```{r example-misc, exercise = TRUE}
x <- 7
x^2 + 1
y <- cos(x)
```

```{r example-misc-check}
test_1 <- find_assignment("x", "couldn't find assignment to x")
test_2 <- check_value(match_number(7)) # looks at value of statement
test_3 <- find_value(50)
test_4 <- find_call("cos()", "didn't see the cos() function being used")
test_5 <- find_call("x^2", "you didn't square x")
test_6 <- find_call("x^2 + 1", "you should have added 1 to x^2")
test_7 <- check_argument("cos(grab_this)", match_number(7))
test_7a <- find_assignment("y", "remember to name the object cos(x) as y")
test_8 <- check_value(match_number(50))
test_9 <- check_value(match_number(cos(7)))

USER_CODE %>% test_1 %>% test_2 %>% then %>% test_5 %>% inside %>% test_6 %>% test_8
# Explanation
# test_1 identifies the line where assignment to x was made
# test_2 checks whether the value produced by the line in test_1 is 7
# the "then" says look at the following lines
# test_5 makes sure x was squared. The "inside" means that test_6 is restricted to 
# the line that test_5 identified. 
# Finally, test_8 checks that the value of this line is 50

USER_CODE %>% test_3 %>% inside %>% test_5 %>% test_6 %>% test_8
# Explanation
# Another way of checking that x^2 + 1 is the statement producing the value 50

USER_CODE %>% test_4 %>% test_7 %>% test_7a %>% test_9
# Looks at the line in which cos() is used
# Note that match_number() is used in test_9 so that tolerant numerical comparison 
# will be applied
```


