---
title: "Examples of Code-Checking using tutor and checkr"
output: html_document
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tutor)
library(ggplot2)
library(checkr)

# A simple checker function

# to put the info in a file
# knitr::opts_chunk$set(exercise.checker = checkr::check_info_to_file)

# to process it in the Rmd document
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

As part of developing the `checkr` user interface, I'm implementing a variety R-related exercises. The point is to see whether concise, transparent, and useful checks can be written, and figure out what new facilities are needed to support such checks.

The exercises in this document are derived from <http://r-exercises.com>. In some cases, I've broken them into simpler parts.

[[Note in draft]]: Idea for example exercises. See <http://r-exercises.com/2016/11/28/data-frame-exercises-vol-2/>

## First bunch

a. Create a vector named `Id` that has contents `1 1 1 2 2 2 3 3 3 4 4 4`. Use the `rep()` function to do this.
```{r bunch-1-a, exercise = TRUE, echo = FALSE}

```

```{r bunch-1-a-solution, echo = FALSE}
Id <- rep(1:4, each = 3)
```

```{r bunch-1-a-hint-1, echo = FALSE}
1:4
```

```{r bunch-1-a-hint-2, echo = FALSE}
rep(1:4, ___ = 3)
```

```{r bunch-1-a-check, echo = FALSE}
# Simple test to see if it was done the way we wanted
test_0 <- fcall("c(1,1,1,2,2)", "Use `rep()` for this exercise, not `c()`", mistake = TRUE)
test_1 <- fcall("rep()", "remember to use the `rep()` function!")
test_2 <- fcall("whatever <- whatever", "give the result a name.")
test_3 <- in_names('Id', "give the result the name `Id`.")
test_4 <- in_statements(regex = "each *=", message = "use the `each = ` argument to `rep()`")
test_5 <- check_argument("rep(whatever, each = grab_this)", match_number(3))
test_all <- fcall("rep(eval(1:4), each = 3)", message = 
                  "some hints: use `rep()` with 1:4 as an input", 
                  diag = TRUE)
test_result <- check_value(match_vector(rep(1:4, each = 3), diag = TRUE), "the output value is not correct")
USER_CODE %>% test_0 %>% test_1 %>% test_2 %>% test_3 %>% test_4 %>% test_5 %>% test_all %>% test_result
```



b. Create a vector named `Letter` that contains `"a" "b" "c" "a" "b" "c" "a" "b" "c" "a" "b" "c"`
```{r bunch-1-b, exercise = TRUE, echo = FALSE}

```

```{r bunch-1-b-solution, echo = FALSE}
Letter <- rep(c("a","b","c"), each = 4)
```

```{r bunch-1-b-hint-1, echo = FALSE}
c("a", "b", "c")
```

```{r bunch-1-b-hint-2, echo = FALSE}
rep(___, each = 3)
```

```{r bunch-1-b-check, echo = FALSE}
# Simple test to see if it was done the way we wanted
test_0 <- fcall("rep()", "Use `rep()` for this exercise")
test_1 <- fcall("whatever <- whatever", "give the result a name.")
test_2 <- in_names('Letter', "give the result the name `Letter`.")
test_3 <- in_statements(regex = "each *=", message = "use the `each = ` argument to `rep()`")
test_4 <- check_argument("rep(whatever, each = grab_this)", match_number(4))
test_5 <- fcall("rep(eval(letters[1:3]), each = 4)", message = 
                  "some hints: use `rep()` with the character vector 'a', 'b', 'c' as an input", 
                  diag = TRUE)
test_result <- check_value(match_vector(rep(letters[1:3], each = 4)), "the output value is not correct")
USER_CODE %>% test_0 %>% test_1 %>% test_2 %>% test_3 %>% test_4 %>% test_result
```


c. You've constructed `Id` and `Letter` in the previous exercises. Now create two more vectors:
    - `x` which will be evenly spaced numbers between 1 and 43. `x` will have the same length as `Id`.
    - `y` which will be similar to `x`, but will consist of evenly spaced numbers between -20 and 0.
    
Once you have constructed `x` and `y`, make a data frame called `df` that contains `x`, `y`, `Id` and `Letter` as columns. The variable names should be `x`, `y`, `Id`, and `Letter`.

```{r bunch-1-c, exercise = TRUE, echo = FALSE}

```

```{r bunch-1-c-solution, echo = FALSE}
Id <- rep(1:4, each = 3)
xx <- seq(1, 43, along.with=Id)
y <- seq(-20,0, along.with=Id)
Letter <- rep(c("a", "b", "c"), 4)
df <- data.frame(Id, Letter, xx, y)
```

```{r bunch-1-c-check, echo = FALSE}
test_1 <- in_names("df", "The data frame should be called 'df'")
test_2 <- check_value(
  match_data_frame(df, names_match = TRUE, nrow = TRUE, classes = TRUE), 
                   paste("the result should look like \n", paste(capture.output(print(df)), collapse = "\n") ))
USER_CODE %>% test_1 %>% test_2

```

## Example 1

Modify the code to add two and two:

```{r, example_0, exercise = TRUE}
1 + 3
```

```{r example_0-solution}
2 + 2
```

```{r example_0-check}
match_values(USER_CODE, SOLN_CODE,
             res = in_statements(regex="+"),
             b = fcall("whatever + grabthis", "Second argument to +"),
             same_num(res))

# test_0 <- fcall("whatever + whatever", "use addition (+)")
# test_1 <- fcall("2 + whatever", "first argument should be two ")
# test_2 <- fcall("whatever + 2", "second argument should also be two")
# USER_CODE %>% test_0 %>% test_1 %>% test_2 
```
